
<!-- the two formats are html and revealjs -->

# Clicker Questions

to go with <b><a href = "https://mdsr-book.github.io/mdsr3e/" target = "_blank">Modern Data Science with R, 3rd edition</a></b> by Baumer, Kaplan, and Horton.  

Many questions taken directly from <a href = "https://www.w3schools.com/quiztest/quiztest.asp?qtest=SQL" target = "_blank">w3schools SQL quiz</a>.

<!--add these https://www.javaguides.net/2023/07/sql-quiz.html and
https://testbook.com/objective-questions/mcq-on-sql--5eea6a0939140f30f369da8c-->

```{=html}
<style>
.reveal ol ol {
   list-style-type: lower-alpha;
}
</style>
```


```{r}
#| echo: false
#| message: false
#| warning: false

# figure options
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
  fig.width = 10, fig.asp = 0.618, out.width = "90%",
  fig.retina = 3, dpi = 300, fig.align = "center"
)

library(tidyverse)

# Make sure to put a space before and after every slide break "---"

```

---

1. What is a **SQL** server?.[^1]
   (a) A relational database management system.
   (b) A software whose main purpose is to store and retrieve data.
   (c) A highly secure server and does not allow any database file manipulation during execution.
   (d) All of the above.

[^1]: a. A relational database management system.


---

2. When was SQL created?[^2]
   (a) 1960s
   (b) 1970s
   (c) 1980s
   (d) 1990s
   (e) 2000s

[^2]: b. The first versions were created in the 1970s and called SEQUEL (Structured English QUEry Language).  c. SQL came about in particular systems in the 1980s.
   
---

3. What type of databases is SQL designed for?[^3]

   (a) hierarchical database management systems.
   (b) network database management systems.
   (c) object-oriented database management systems.
   (d) relational database management systems.

[^3]: d. relational database management systems.

---

4. Which is bigger:[^4]
   (a) computer's hard drive / storage
   (b) computer's memory / RAM

[^4]: a. computer's hard drive / storage

---

5. Where are each stored?[^5]
   (a) SQL `tbl` and R `tibble` both in storage
   (b) SQL `tbl` and R `tibble` both in memory
   (c) SQL `tbl` in storage and R `tibble` in memory
   (d) SQL `tbl` in memory and R `tibble` in storage
   
[^5]: c. SQL `tbl` in storage and R `tibble` in memory

---

6. Which SQL clause is used to extract data from a database?[^6]
   (a) OPEN
   (b) EXTRACT
   (c) SELECT
   (d) GET

[^6]: c. SELECT

---

7. With SQL, how to you retrieve a column named "FirstName" from a table named "Persons"?[^7]
   (a) SELECT Persons.FirstName
   (b) EXTRACT FIRSTNAME FROM Persons
   (c) SELECT FirstName FROM Persons
   (d) SELECT "FirstName" FROM "Persons"

[^7]: c. SELECT FirstName FROM Persons

---

8. With SQL, how do you select all the columns from a table named "Persons"?[^8]
   (a) SELECT Persons
   (b) SELECT * FROM Persons
   (c) SELECT [all] FROM Persons
   (d) SELECT *.Persons

[^8]: b. SELECT * FROM Persons

---

9. With SQL, how can you return the number of records in the "Persons" table?[^9]
   (a) SELECT COLUMNS(*) FROM Persons
   (b) SELECT COUNT(*) FROM Persons
   (c) SELECT NO(*) FROM Persons
   (d) SELECT LEN(*) FROM Persons

[^9]: b. SELECT COUNT(*) FROM Persons

---

10. With SQL, how do you select all the records from a table named "Persons" where the value of the column "FirstName" is "Peter"?[^10]
   (a) SELECT * FROM Persons WHERE FirstName <> 'Peter'
   (b) SELECT * FROM Persons WHERE FirstName = 'Peter'
   (c) SELECT * FROM Persons WHERE FirstName == 'Peter'
   (d) SELECT [all] FROM Persons WHERE FirstName LIKE 'Peter'
   (e) SELECT [all] FROM Persons WHERE FirstName = 'Peter'
   
[^10]: b. SELECT * FROM Persons WHERE FirstName = 'Peter'

---

11. With SQL, how do you select all the records from a table named "Persons" where the "FirstName" is "Peter" and the "LastName" is "Jackson"?[^11]
   (a) SELECT FirstName = 'Peter', LastName = 'Jackson' FROM Persons
   (b) SELECT * FROM Persons WHERE FirstName <> 'Peter' AND LastName <> 'Jackson'
   (c) SELECT * FROM Persons WHERE FirstName = 'Peter' AND LastName = 'Jackson'
   (d) SELECT * FROM Persons WHERE FirstName == 'Peter' AND LastName == 'Jackson'

[^11]: c. SELECT * FROM Persons WHERE FirstName = 'Peter' AND LastName = 'Jackson'

---

12. Which operator selects values within a range?[^12]
    (a) BEWTEEN
    (b) WITHIN
    (c) RANGE

[^12]: a. BEWTEEN

---

13. With SQL, how do you select all the records from a table named "Persons" where the "LastName" is alphabetically between (and including) "Hansen" and "Pettersen"?[^13]
    (a) SELECT LastName > 'Hansen' AND LastName < 'Pettersen' FROM Persons
    (b) SELECT * FROM Persons WHERE LastName BETWEEN 'Hansen' AND 'Pettersen'
    (c) SELECT * FROM Persons WHERE LastName > 'Hansen' AND LastName < 'Pettersen'

[^13]: b. SELECT * FROM Persons WHERE LastName BETWEEN 'Hansen' AND 'Pettersen'

---

14. Which SQL statement returns only different values?[^14]
    (a) SELECT UNIQUE
    (b) SELECT DISTINCT
    (c) SELECT DIFFERENT

[^14]: b. SELECT DISTINCT

---

15. Which SQL keyword is used to sort the result-set?[^15]
    (a) ORDER BY
    (b) ORDER
    (c) SORT
    (d) SORT BY
 
[^15]: a. ORDER BY

---

16. With SQL, how can you return all the records from a table named "Persons" sorted descending by "FirstName"?[^16]
    (a) SELECT * FROM Persons ORDER FirstName DESC
    (b) SELECT * FROM Persons SORT 'FirstName' DESC
    (c) SELECT * FROM Persons ORDER BY FirstName DESC
    (d) SELECT * FROM Persons SORT BY 'FirstName' DESC

[^16]: c. SELECT * FROM Persons ORDER BY FirstName DESC

---

17. The OR operator displays a record if ANY conditions listed are true. The AND operator displays a record if ALL of the conditions listed are true.[^17]
    (a) TRUE
    (b) FALSE 

[^17]: a. TRUE

---

18. In order to SELECT the records with foods that are either green or yellow fruit:[^18] 
    (a) ... WHERE type = 'fruit' AND color = 'yellow' OR color = 'green'  
    (b) ... WHERE (type = 'fruit' AND color = 'yellow') OR color = 'green'  
    (c) ... WHERE type = 'fruit' AND (color = 'yellow' OR color = 'green')  
    (d) ... WHERE type = 'fruit' AND color = 'yellow' AND color = 'green'  
    (e) ... WHERE type = 'fruit' AND (color = 'yellow' AND color = 'green') 
   
[^18]: c. ... WHERE type = 'fruit' AND (color = 'yellow' OR color = 'green') 


---

19. What is the purpose of a `JOIN`?[^19]  
    (a) it filters the rows returned by the `SELECT` statement.
    (b) it specifies the columns to be retrieved.
    (c) it combines rows from two or more tables based on a related column.
    (d) it orders the results in ascending or descending order.

[^19]: c. it combines rows from two or more tables based on a related column.

---

20. What is the purpose of the UNION operator in SQL?[^20]
    (a) it combines the results of two or more `SELECT` statements. 
    (b) it performs a pattern match on a string.
    (c) it retrieves the maximum value in a column.
    (d) it filters the rows returned by the `SELECT` statement.

[^20]: a. it combines the results of two or more `SELECT` statements.

---

21. What is the purpose of the `INNER JOIN` in SQL?[^21]
    (a) it retrieves the maximum value in a column.
    (b) it combines rows from two or more tables based on a related column. 
    (c) it filters the rows returned by the SELECT statement.
    (d) it performs a pattern match on a string.

[^21]: b. it combines rows from two or more tables based on a related column.

---

22. What is the purpose of the `LEFT JOIN` in SQL?[^22]
    (a) it combines rows from two or more tables based on a related column.
    (b) it retrieves the maximum value in a column.
    (c) it filters the rows returned by the `SELECT` statement. 
    (d) it performs a pattern match on a string.

[^22]: a. it combines rows from two or more tables based on a related column.

---

23. `RIGHT JOIN` keeps all the rows in ...?[^23]  
    (a) the first table.
    (b) the second table.
    (c) both tables.
    (d) neither table

[^19]: a. the first table

---


<!--look at exercises: https://github.com/STAT545-UBC/STAT545-UBC-original-website/blob/master/block022_regular-expression.md

which reg expr matches all countries with "ee"

countries with "i" or "t" and ends in "land"; has "ee"; continents with "o"

can use flights data for cities with particular names-->



17. `grep("q[^u]", very.large.word.list)` would not match which of the following?[^17]
    (a) Iraqi
    (b) Iraqian
    (c) Iraq
    (d) zaqqun (tree that "springs out of the bottom of Hell", in the Quran)
    (e) Qantas (the Australian airline)
    
[^17]: neither c. nor e. would match.

---

17. Which of the following regex would match to both "grey" and "gray"?[^17]
    (a) "gr[ae]y"
    (b) "gr(a|e)y"
    (c) "gray | grey"
    (d) "gr[a|e]y"
    (e) some / all of the above -- which ones?

[^17]: e. all of the above. Inside a character class `|` is a normal character and would therefore match "grey" and "gray" and "gr|y".  Which is not what we want, but would work to match both "grey" and "gray".


---

17. What will the result be for the following code?[^17]  
    (a) 10
    (b) 1
    (c) 0
    (d) NA

```{r}
#| eval: false
#| echo: true
str_extract("My dog is 10 years old", "\\d")
``` 
    
[^17]: b. 1 (because `\d` matches only a single digit).


---

17. What will the result be for the following code?[^17]
    (a) .
    (b) Episode 2: The pie whisperer. (4 August 2015)
    (c) Episode
    (d) E

```{r}
#| eval: false
#| echo: true
str_extract("Episode 2: The pie whisperer. (4 August 2015)", ".")
```

[^17]: d. E (because `.` matches anything, and returns only a single character).

---

17. What will the result be for the following code?[^17]
    (a) .
    (b) Episode 2: The pie whisperer. (4 August 2015)
    (c) Episode
    (d) E

```{r}
#| eval: false
#| echo: true
str_extract("Episode 2: The pie whisperer. (4 August 2015)", ".+")
```

[^17]: b. Episode 2: The pie whisperer. (4 August 2015) (because `.` matches anything, and with the `+` it returns multiple characters).

---

17. What will the result be for the following code?[^17]
    (a) .
    (b) Episode 2: The pie whisperer. (4 August 2015)
    (c) Episode
    (d) E

```{r}
#| eval: false
#| echo: true
str_extract("Episode 2: The pie whisperer. (4 August 2015)", "\\.")
```

[^17]: a. . (because `\.` matches the period, .).


---

17. Which operator is used to search for a specified pattern in a column?[^17]
    (a) LIKE
    (b) GET
    (c) FROM

[^17]: a. LIKE

---

18. With **SQL**, how do you select all the records from a table named "Persons" where the value of the column "FirstName" starts with an "a"?[^18]
    (a) SELECT * FROM Persons WHERE FirstName LIKE 'a%'
    (b) SELECT * FROM Persons WHERE FirstName = '%a%'
    (c) SELECT * FROM Persons WHERE FirstName LIKE '%a'
    (c) SELECT * FROM Persons WHERE FirstName = 'a'

[^18]: a. SELECT * FROM Persons WHERE FirstName LIKE 'a%'

---

19. Which SQL statement is used to create a database table called 'Customers'?[^19]
    (a) CREATE DATABASE TAB Customers
    (b) CREATE TABLE Customers
    (c) CREATE DATABASE TABLE Customers
    (d) CREATE DB Customers

[^19]: b. CREATE TABLE Customers

---

20. Which **SQL** statement updates data in a database?[^20]
    (a) SAVE AS 
    (b) MODIFY
    (c) SAVE
    (d) UPDATE

[^20]: d. UPDATE

---

21. Which **SQL** statement deletes data from a database?[^21]
    (a) REMOVE
    (b) DELETE
    (c) COLLAPSE

[^21]: b. DELETE

---

22. The NOT NULL constraint enforces a column to not accept NULL values.[^22]
    (a) FALSE
    (b) TRUE

[^22]: b. TRUE

---

23. Which **SQL** statement inserts new data in a database?[^23]
    (a) ADD RECORD
    (b) INSERT INTO
    (c) ADD NEW
    (d) INSERT NEW 
 
[^23]: b. INSERT INTO

---

24. With **SQL**, how can you insert a new record into the "Persons" table?[^24]
    (a) INSERT INTO Persons VALUES ('Jimmy', 'Jackson')
    (b) INSERT ('Jimmy', 'Jacskon') INTO Persons
    (c) INSERT VALUES ('Jimmy', 'Jackson') INTO Persons

[^24]: a. INSERT INTO Persons VALUES ('Jimmy', 'Jackson')

---

25. With **SQL**, how can you insert "Olsen" as the "LastName" in the "Persons" table?[^25]
    (a) INSERT INTO Persons (LastName) VALUES ('Olsen')
    (b) INSERT INTO Persons ('Olsen) INTO LastName
    (c) INSERT ('Olsen') INTO Persons (LastName)
 
[^25]: a. INSERT INTO Persons (LastName) VALUES ('Olsen')

---

26. How can you change "Hansen" into "Nilsen" in the "LastName" column in the Persons table?[^26]
    (a) MODIFY Persons SET LastName='Nilsen' WHERE LastName='Hansen'
    (b) UPDATE Persons SET LastName='Hansen' INTO LastName='Nilsen'
    (c) MODIFY Persons SET LastName='Hansen' INTO LastName='Nilsen'
    (d) UPDATE Persons SET LastName='Nilsen' WHERE LastName='Hansen' 

[^26]: d. UPDATE Persons SET LastName='Nilsen' WHERE LastName='Hansen' 

---

27. With **SQL**, how can you delete the records where the "FirstName" is "Peter" in the Persons Table?[^27]
    (a) DELETE FROM Persons WHERE FirstName='Peter'
    (b) DELETE FirstName='Peter' FROM Persons
    (c) DELETE ROW FirstName='Peter' FROM Persons

[^27]: a. DELETE FROM Persons WHERE FirstName='Peter'

---




